Community-Conditioned Language Models

### 2020-11-23 paper/paper.tex
typography

\begin{table}
  \centering
  \input{floats/comm_sim.tex}
  \caption{Pearson's r between the pairwise similarity of community vectors
  in the CCLM models and the membership-based embedding of \citet{Kumar2018}.
  ($p<0.001$ for all models).
  }
  \label{tab:pairwise-comm-sim}
\end{table}

>>>>

\begin{table}
  \centering
  \input{floats/comm_sim.tex}
  \caption{Pearson's $r$ between the pairwise similarity of community vectors
  in the CCLM models and the membership-based embedding of \citet{Kumar2018}.
  ($p<0.001$ for all models).
  }
  \label{tab:pairwise-comm-sim}
\end{table}
